Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-05-15 mtjournal.tex
\bar{\mu} now always used without following parens
per Mari's suggestion

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}(m)$ and $\bar{\mu}(\textrm{HTER})$ (rather than measure
$m$ and HTER), where $\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}(m(t_i)) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\endnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. The results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in the
  Pearson's $r$ tests, and we use mean-removal throughout this work
  instead.}

@@

As discussed in section~\ref{sec:paradigm}, we report correlations
here between $\bar{\mu}(m)$ and $\bar{\mu}(\textrm{HTER})$, rather
than $m$ and HTER directly, to abstract away from variations in the
underlying documents.

>>>>

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}m$ and $\bar{\mu}\textrm{HTER}$ (rather than measure
$m$ and HTER), where $\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}m(t_i) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\endnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. The results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in the
  Pearson's $r$ tests, and we use mean-removal throughout this work
  instead.}

@@

As discussed in section~\ref{sec:paradigm}, we report correlations
here between $\bar{\mu}m$ and $\bar{\mu}\textrm{HTER}$, rather
than $m$ and HTER directly, to abstract away from variations in the
underlying documents.
